\systemnamenospace: Head Orientation-Based Selection\\in Physical Spaces

### 2014-08-14 doc/sui14/iteration1.tex
update i1 participant gender

\subsection{Method}
We deployed 10 wireless nodes in an indoor environment (Figure~\ref{fig:targeting-study-layout}), each with a number ID and a letter representing the name. For the study, \changes{we recruited 16 participants from our institution (8 males and 6 females) by email.} \changes{Participants included undergraduate and graduate students, as well as university staff. Their educational backgrounds included Information Science (6), Engineering (4), Math and Science (4), Design (1), Others(1).}  \changes{14} had never used Google Glass before, so we offered a tutorial before the experiment in order to introduce the device. Four participants wore prescription glasses, which makes Glass more cumbersome to use and adjust and may have affected their task performance. In this study, the IR LED was fixed and not repositionable as shown in Figure~\ref{fig:glass}.

>>>>

\subsection{Method}
We deployed 10 wireless nodes in an indoor environment (Figure~\ref{fig:targeting-study-layout}), each with a number ID and a letter representing the name. For the study, \changes{we recruited 16 participants from our institution (9 males and 7 females) by email.} \changes{Participants included undergraduate and graduate students, as well as university staff. Their educational backgrounds included Information Science (6), Engineering (4), Math and Science (4), Design (1), Others(1).}  \changes{14} had never used Google Glass before, so we offered a tutorial before the experiment in order to introduce the device. Four participants wore prescription glasses, which makes Glass more cumbersome to use and adjust and may have affected their task performance. In this study, the IR LED was fixed and not repositionable as shown in Figure~\ref{fig:glass}.
